Untitled

### 2024-09-05 code/manuscript_analysis.Rmd
remove winsoring, cleaner estimation of distance effects

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) #%>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
}

model <- did2s(
      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) #%>%  mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.close <- rbind(TEs.strat.close, data.frame(model$coeftable)[1,])
}

cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:5),]
```

@@

did2s(
      data = df.spill3 %>% #filter((Dist > quantile(Dist, 0.4) & Dist < quantile(Dist, 0.6) & Att > 0) | Att == 0 ) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

mean(df.spill3[df.spill3$Dist < quantile(df.spill3$Dist, probs = c(0.15)),]$Dist)
mean(df.spill3[df.spill3$Dist > quantile(df.spill3$Dist, probs = c(0.85)),]$Dist)

df.spill3 %>% filter(Att > 0 & Dist < 0.33476343 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
df.spill3 %>% filter(Att > 0 & Dist > 157.1606 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())

df.spill3 %>% 
  filter(Year == Att - 1) %>% 
  mutate(EstimatedChange = 6 + -0.039*Dist) %>% 
  summarise(sum(abs(EstimatedChange)) / sum(Total.Hours))

>>>>

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)),# %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        #mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
        #                            ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 10:19){
  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) #%>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
}

model <- did2s(
      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)),# %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
       # mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
        #                            ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 10:19){
  df.temp <- df.spill3 %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) #%>%  mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.close <- rbind(TEs.strat.close, data.frame(model$coeftable)[1,])
}

cbind(colnames(df.spill3)[c(30, 10:19)], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(7:11, 2, 1, 3:6),]

did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Outcome = ifelse(Sites == 0, 0, Schedule / Sites)), 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
       # mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
        #                            ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

did2s(
      data = df.spill3, #%>% #filter((Dist > quantile(Dist, 0.4) & Dist < quantile(Dist, 0.6) & Att > 0) | Att == 0 ) %>% 
        #mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
       #                             ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

dist.close <- mean(df.spill3[df.spill3$Dist < quantile(df.spill3$Dist, probs = c(0.15)),]$Dist)
dist.far <- mean(df.spill3[df.spill3$Dist > quantile(df.spill3$Dist, probs = c(0.85)),]$Dist)

df.spill3 %>% filter(Att > 0 & Dist < quantile(df.spill3$Dist, probs = c(0.15)) & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
df.spill3 %>% filter(Att > 0 & Dist > quantile(df.spill3$Dist, probs = c(0.85)) & Year == Att - 1) %>% summarise(sum(Total.Hours), n())

df.spill3 %>% 
  filter(Year == Att - 1) %>% 
  mutate(EstimatedChange =  TEs.strat.close[2,1] + (TEs.strat.far[2,1] - TEs.strat.close[2,1]) / (dist.far - dist.close)*Dist) %>% 
  summarise(sum(abs(EstimatedChange)) / sum(Total.Hours))
